\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{listings}
\usepackage{xcolor}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    pdftitle={API Documentation},
}

\lstset{
    basicstyle=\ttfamily\small,
    breaklines=true,
    backgroundcolor=\color{gray!10},
    frame=single,
    rulecolor=\color{black!30},
    xleftmargin=10pt,
    xrightmargin=10pt
}

\title{\textbf{Viniyog One: API Documentation}}
\author{System Integration \& Security Specifications}
\date{\today}

\begin{document}

\maketitle

\section{Overview}
Viniyog One utilizes FastAPI to provide a robust, asynchronously capable RESTful API for executing Retrieval-Augmented Generation (RAG) processes. All endpoints are fortified behind a hierarchical Role-Based Access Control (RBAC) middleware ensuring strict banking security constraints.

\section{Permission Hierarchy}
All active endpoints require the \texttt{X-User-Role} HTTP header containing a valid system role.
\begin{itemize}
    \item \textbf{user:} Can execute standard retrieval queries.
    \item \textbf{evaluator:} Authorized to execute extensive trace tools, diagnostic evaluations, and latency benchmarking.
    \item \textbf{admin:} Full internal read access to system logs, monitoring paths, and ring-buffer retrieval states.
    \item \textbf{system:} An isolated internal service role. It operates solely to mint and consume short-lived Knowledge Base fallback tokens.
\end{itemize}

\section{Core Endpoints}

\subsection{1. \texttt{POST /query}}
\textbf{Description:} Initiates a standard user query against the entire RAG pipeline. The return envelope encapsulates the LLM response alongside the exact snippet-level vector attributions.
\begin{itemize}
    \item \textbf{Required Role:} \texttt{user}
    \item \textbf{Request Example:}
\begin{lstlisting}[language=json]
{
  "query": "What is the PM Mudra Yojana eligibility?"
}
\end{lstlisting}
    \item \textbf{Response Example (200 OK):}
\begin{lstlisting}[language=json]
{
  "query": "What is the PM Mudra Yojana eligibility?",
  "answer": "The PM Mudra Yojana provides loans to non-corporate...",
  "sources": [
    {
      "content": "...relevant context snippet...",
      "metadata": {"scheme_name": "PMMY"}
    }
  ]
}
\end{lstlisting}
\end{itemize}

\subsection{2. \texttt{POST /query/debug}}
\textbf{Description:} Returns an unfiltered, verbose pipeline trace displaying internal chunking extraction metrics, similarity cosine scores, and pre/post-generation hallucination evaluations.
\begin{itemize}
    \item \textbf{Required Role:} \texttt{evaluator}
\end{itemize}

\subsection{3. \texttt{POST /evaluate}}
\textbf{Description:} Accepts batched query arrays for pipeline testing. Output structures aggregate SLA constraints (e.g., Average Groundedness Scores, Hallucination and/or Fallback Threshold Rates, and total Latency overhead).
\begin{itemize}
    \item \textbf{Required Role:} \texttt{evaluator}
\end{itemize}

\section{Infrastructure Endpoints}

\subsection{4. \texttt{GET /health}}
\textbf{Description:} Unauthenticated public check. Responsible for polling sub-component capacities including vector stores, LLM endpoint availability, and SQLite mounts. Designed for Kubernetes liveness probes.
\begin{itemize}
    \item \textbf{Required Role:} None (Public)
\end{itemize}

\subsection{5. \texttt{GET /retrieval/logs}}
\textbf{Description:} Outputs complete historical query logs including embedding similarity boundaries, and active fallback instances. Governed entirely by an internal ring-buffer cache.
\begin{itemize}
    \item \textbf{Required Role:} \texttt{admin}
\end{itemize}

\section{Internal Security Endpoints (Token-Gated)}

\subsection{6. \texttt{POST /kb/token}}
\textbf{Description:} Mints a specialized \texttt{HS256}-signed JSON Web Token specifically embedding \texttt{purpose: kb\_access} logic. Configured with a rigorous 1-minute TTL.
\begin{itemize}
    \item \textbf{Required Role:} \texttt{system}
\end{itemize}

\subsection{7. \texttt{POST /kb/fetch}}
\textbf{Description:} High-security Knowledge Base fallback route. Triggers only when the initial LLM output violates the strict $0.85$ bounded hallucination constraint. Extracts verified strings natively from the FTS5 SQLite database.
\begin{itemize}
    \item \textbf{Required Role:} \texttt{system} (Mandates \texttt{Bearer token} extracted from \texttt{/kb/token})
\end{itemize}

\end{document}
