\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{enumitem}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    pdftitle={System Architecture Documentation},
}

\title{\textbf{Viniyog One: System Architecture Documentation}}
\author{Architecture, Control Flow, and Pipeline Specifications}
\date{\today}

\begin{document}

\maketitle

\section{System Architecture}

The Viniyog One Enterprise RAG system is a multi-stage architecture enforcing strict semantic grounding mechanisms specifically built for the banking paradigm. 

\subsection{Core Components}
\begin{itemize}
    \item \textbf{FastAPI Gateway}: Asynchronous REST handler intercepting calls and applying Header-based RBAC constraints.
    \item \textbf{Bi-Encoder Vector DB}: \texttt{BAAI/bge-large-en-v1.5} dense representation logic mounted over a locally persisting \texttt{ChromaDB}.
    \item \textbf{Knowledge Base Fallback}: Authoritative, isolated SQLite Database with FTS5 keyword lookups. Token-gated to prevent unstructured data exfiltration.
    \item \textbf{Generative Module}: Google Gemini 2.0 Flash leveraging structured JSON schemas for determinism.
\end{itemize}

\subsection{Architectural Flow}
\begin{verbatim}
[Client Request] ----> [FastAPI Gateway]
                              |
                     (RBAC Validation)
                              |
                    [ Router /query/ ] ----> [RAG Pipeline]
                                                    |
[ChromaDB Top-10] <---- (Retrieve) -----------------+
       |
[Cross-Encoder Top-3]
       |
[Gemini Structured Generation]
       |
       +----> (Groundedness >= 0.85) ----> [Format Output] ----> [User]
       |
       +----> (Groundedness < 0.85) ----> [KB Fallback Mint]
                                                  |
                                          [SQLite FTS5 DB]
                                                  |
                                          [Format Output] ----> [User]
\end{verbatim}

\section{Data Flow Explanation}
The foundational data flow adheres strictly to: \textbf{The LLM is NOT the source of truth.} All generation is contextualized against dynamic injection.

\begin{itemize}
    \item \textbf{Data Origin}: Source definitions originate in robust structures (\texttt{banking\_schemes.json} or \texttt{.csv}). The Ingestion layer (\texttt{ingestion\_service.py}) transforms tabular schemas natively into descriptive prose (e.g., converting ``7.5\% Return'' to ``Interest rate is 7.5\% per annum'') optimized for MTEB representation.
    \item \textbf{Query Time Operation}: Vector distances mapped dynamically. Bi-encoders retrieve a broad Top-10 span which prevents data loss on edge-terminology logic. Then heavy lifting cross-encoder evaluation reranks the final contexts. Finally, constraints map exact attributions to the LLM generation block via XML styling bounds \texttt{<source id="X">}.
\end{itemize}

\section{Chunking Strategy Justification}
The BRD strictly requested evaluation between sliding/fixed/semantic operations. We bypassed arbitrary limits in favor of complex \textbf{Semantic Chunking}.

\begin{itemize}
    \item \textbf{Why}: Traditional Fixed-Window tokens arbitrarily split sentences down the middle.
    \item \textbf{Methodology}: Our engine leverages sliding baseline calculations over continuous cosine similarity changes. Boundary changes below 0.8 automatically split chunks preserving localized structural semantic alignment. Post-processing restricts the ultimate context footprint purely into a \texttt{256 - 512} token limit matching native banking layout documents.
\end{itemize}

\section{Retrieval Design Decisions}
A wide-to-narrow mechanism controls precision drops common to basic models.
\begin{itemize}
    \item At \texttt{Top-K = 10}, ChromaDB achieves maximal \textbf{Recall}, netting related edge domains.
    \item We augment pure retrieval via \texttt{cross-encoder/ms-marco-MiniLM-L-6-v2}. This model processes queries and passages contiguously to evaluate cross-attention (as opposed to dual dense representation independent mapping).
    \item This distills the Top-10 down to a heavily scrutinized isolated \textbf{Top-3} eliminating noise before GenAi computation, lowering hallucination risks.
\end{itemize}

\section{Hallucination Detection Logic}
Rather than the multi-step delayed calls characterizing legacy validation systems, Viniyog operates \textbf{Single-Pass Evaluative RAG}.

\begin{itemize}
    \item Gemini is forced to generate a \texttt{Pydantic GroundedResponse}.
    \item Rather than generate simple prose, the structure must emit the generated answer \textit{AND} atomistically evaluate its component facts via \texttt{self\_evaluated\_groundedness}.
    \item Combined with localized heuristic validations (entity tracking and numerical overlap validations), scores compute synchronously. Any output failing a strict \texttt{0.85} limitation is caught and discarded gracefully. False positives fall back to authoritative DB endpoints reliably avoiding hallucination damage completely.
\end{itemize}

\section{KB Token Mechanism}
Token-layer restrictions operate based on \texttt{JWT (HS256)} lifecycle mechanics.
\begin{itemize}
    \item A failed LLM hallucination boundary triggers the system infrastructure account to POST \texttt{/kb/token}. This issues a stateless token restricted explicitly to generating payloads on \texttt{/kb/fetch}.
    \item Tokens expire in 60s, completely isolating the source-of-truth banking SQLite database from being dumped improperly by untethered or external agents attempting to scrape backend APIs.
\end{itemize}

\section{Limitations and Trade-offs}
\begin{itemize}
    \item \textbf{In-Memory Volatility}: To adhere to immediate testability for the assessment, the ring buffer for \texttt{/retrieval/logs} operates ephemerally in-memory. Standard production runs mandate a Redis drop-in.
    \item \textbf{SQLite Concurrency constraints}: By building an embeddable architecture directly serving \texttt{.db} assets we ensure universal code distribution, but production scale multi-write mechanics would require native DB adaptations \texttt{(i.e., PostgreSQL)}.
\end{itemize}

\end{document}
